Best Practices for Multiple Alchemical Free Energy Calculations [Article v\versionnumber]

### 2025-05-11 paper/manuscript.tex
Update manuscript.tex

%SIS
Subgraph isomorphism solver (SIS)-based maximum common substructure (MCSS) search methods currently represent the most widely used approach for addressing atom mapping challenges, at the current timepoint. Several cheminformatics tools implementing these solutions are readily available, including pmx~\cite{gapsys2015pmx}, LOMAP~\cite{liu2013lead}, FESetup~\cite{loeffler2015fesetup}, ProtoCaller~\cite{suruzhon2020protocaller}, and SMArt~\cite{petrov2021perturbation}.

@@

\paragraph{Perturbation maps}
\tocsectioncomment{Perturbation maps paragraph: @Mary Pitman/ @Jenke Scheen/ OpenFE team to update discussion of perturbation maps?}
Based on the input ligand series, a perturbation map or network can be planned. Recent heuristics have shown the more connected the perturbation network the better. However, there is a way to optimize network structure while minimizing the number of perturbations that need to be computed reducing the resulting computational cost~\cite{yang2020optimal,xu2019optimal}. Sometimes the introduction of intermediates that are not part of the original congeneric series are essential to avoid ring breaking, or to deal with perturbations that would otherwise result in large numbers of atoms being inserted or deleted. Some commercial tools have good underlying heuristics but may fail with complicated input, needing user validation in particular when dealing with chiral compounds.

\begin{figure}
    \includegraphics[width=0.95\columnwidth]{figures/fig6_types_of_networks/Figure.pdf}
    \caption{\textbf{Examples of perturbation networks} (\textbf{A}) Star shaped network with the crystal structure in the center. (\textbf{B}) Network with cycle closures (see more on this in Sec.~\ref{sec:are-they-good}). Arrows indicate the direction of the perturbation. Fully converged binding free energy calculations yield binding free energy changes which sum to zero around any closed cycle. However, in practice errors may not sum to zero around closed cycles, providing a way to look for potential sampling problems. Here in (B), green cycles indicate cycles with hypothetically good cycle closure, red those with poor cycle closure. The red arrow indicates a poorly converged simulation that would give rise to bad cycle closures. The diamond indicates the use of a crystallographic binding mode.}
    \label{fig:fig_types_of_networks}
\end{figure}

>>>>

%SIS
Subgraph isomorphism solver (SIS)-based maximum common substructure (MCSS) search methods currently represent the most widely used approach for addressing atom mapping challenges. Several cheminformatics tools implementing these solutions are readily available, including pmx~\cite{gapsys2015pmx}, LOMAP~\cite{liu2013lead}, FESetup~\cite{loeffler2015fesetup}, ProtoCaller~\cite{suruzhon2020protocaller}, and SMArt~\cite{petrov2021perturbation}.

@@

\paragraph{Perturbation maps}
\tocsectioncomment{Perturbation maps paragraph: @Mary Pitman/ @Jenke Scheen/ OpenFE team to update discussion of perturbation maps?}
Based on the input ligand series, a perturbation map or network can be planned. Recent heuristics have shown the more connected the perturbation network the better. However, methods exist to optimize network structure while minimizing the number of perturbations that need to be computed reducing the resulting computational cost~\cite{yang2020optimal,xu2019optimal}. Sometimes the introduction of intermediates that are not part of the original congeneric series are essential to avoid ring breaking, or to deal with perturbations that would otherwise result in large numbers of atoms being inserted or deleted. Some commercial tools have good underlying heuristics but may fail with complicated input, needing user validation in particular when dealing with chiral compounds.

\begin{figure}
    \includegraphics[width=0.95\columnwidth]{figures/fig6_types_of_networks/Figure.pdf}
    \caption{\textbf{Examples of perturbation networks} (\textbf{A}) Star shaped network with the crystal structure in the center. (\textbf{B}) Network with cycle closures (see more on this in Sec.~\ref{sec:are-they-good}). Arrows indicate the direction of the perturbation. Fully converged binding free energy calculations yield binding free energy changes which sum to zero around any closed cycle, and non-closing cycles that do not equal zero to within combined error can indicate potential sampling problems or protocol issues. Here in (B), green cycles indicate cycles with hypothetically good cycle closure, red those with poor cycle closure. The red arrow indicates a poorly converged simulation that would give rise to bad cycle closures. The diamond indicates the use of a crystallographic binding mode.}
    \label{fig:fig_types_of_networks}
\end{figure}
